Empirical normative theories

### 2020-06-23 simple.tex
Started centralizing draft notes

\section{Normative theories}
Sketch: define normative models, using questions, and making claims about DJ. A problem is that models specific to a narrow situation will not offer enough means for falsification. Then define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it. BUT what about a model for only one situation? Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).

\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$, 
with ${\ileadstoe[i]} \subseteq \allhist × \Phi$, 
where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. (Throughout the article, $\N$ includes zero, and note that $\intvl{1, 0} = \emptyset$.)

@@

>>>>

\section{Normative theories}
\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I})$, 
with ${\ileadstoe[i]} \subseteq \allhist × \Phi$, 
where $\allhist = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ denotes all finite sequences of elements in $\allargs$ (including the empty sequence) and $\Phi = \allprops × \set{\text{possible}, \text{sure}}$. (Throughout the article, $\N$ includes zero, and note that $\intvl{1, 0} = \emptyset$.)

@@

\section{Next}
Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.

What about a model for only one situation? Then we need to accept that $q$ can’t be falsified, and accept that it defines the individual (or just assume without proof that it does not).
